Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
section title change.
partially denied.
Wording

Hspec can be used to document the behavior of a system in a way that
is similar to a specification.  All facets of the system should be
described with examples and properties, including every possible
corner case.

@@

We propose to use Doctest and Haddock to test evidence that is useful
as user documentation, and Hspec for evidence that is not useful as
user documentation.

@@

\begin{itemize}
\item We use a preprocessor (http://hackage.haskell.org/package/hspec-discover) to automatically generate this boilerplate.
\end{itemize}

>>>>

Hspec can be used to document the behavior of a system in a way that
is similar to a specification.  All facets of the system should be
described with evidence, including every possible corner case.

@@

We propose to use Doctest and Haddock for evidence that is useful as
user documentation, and Hspec for evidence that is not useful as user
documentation.

@@

\begin{itemize}
\item We use a preprocessor (the {\tt hspec-discover} package) to automatically generate this boilerplate.
\end{itemize}
